A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface

### 2021-09-17 sections/appendix/descrete_event_simulation/main.tex
Add documentation for 3 additional functions

@@

\begin{itemize}
    \item \lstinline[style=pystyle]{build_model}: \textit{Builds a ciw object 
    that represents a model of a queuing network with two waiting spaces.}
    \item \lstinline[style=pystyle]{build_custom_node}: \textit{Build a custom 
    node to replace the default ciw.Node. Inherits from the original ciw.Node 
    class and replaces two methods.}
    \item \lstinline[style=pystyle]{simulate_model}: \textit{Simulate the model
    by using the custom node and returning the simulation object}
    \item \lstinline[style=pystyle]{get_simulated_state_probabilities}: \textit{
    Calculates the vector pi in a dictionary format or an array format}
    \item \lstinline[style=pystyle]{extract_times_from_records}: \textit{Get the
    required times (waiting, service, blocking) out of ciw's records where all 
    individuals are treated the same way}
    \item \lstinline[style=pystyle]{extract_times_from_individuals}: \textit{
    Extract waiting times and service times for all individuals and proceed to 
    extract blocking times for only class 2 individuals}
    \item \lstinline[style=pystyle]{get_list_of_results}: \textit{Modify the 
    outputs so that they are returned in a list format where it is sometimes 
    easier to be used by other functions.}
    \item \lstinline[style=pystyle]{get_multiple_runs_results}: \textit{Get the 
    waiting times, service times and blocking times for multiple runs of the 
    simulation}
    \item \lstinline[style=pystyle]{get_average_simulated_state_probabilities}:
    \textit{This function runs \hfill\break
    get\_simulated\_state\_probabilities for multiple iterations to eliminate 
    any stochasticity from the results}
    \item \lstinline[style=pystyle]
    {get_mean_blocking_difference_between_two_systems}: \textit{Given a 
    predefined proportion of class's 2 arrival rate calculate the mean 
    difference between blocking times of two systems with a given set of 
    parameters}
    \item \lstinline[style=pystyle]{calculate_class_2_individuals_best_response}
    \textit{Obtains the optimal distribution of class 2 individuals such that 
    the blocking times in the two systems are identical and thus minimised}
    \item \lstinline[style=pystyle]
    {extract_total_individuals_and_the_ones_within_target_for_both_classes}:
    \hfill\break \textit{Extract the total number of individuals that pass 
    through the model and the total number of individuals that exit the model 
    within the given target.}
    \item \lstinline[style=pystyle]
    {get_mean_proportion_of_individuals_within_target_for_multiple_runs}: 
    \textit{Get the average proportion of individuals within target by running 
    the simulation multiple times}
\end{itemize}

>>>>

To get the steady state probabilities of the model based on the simulation the
following code can be used:
\begin{lstlisting}[style=pystyle]
    >>> import numpy as np
    >>> import ambulance_game as abg
    >>> simulation_object = abg.simulation.simulate_model(
    ...     lambda_1=1,
    ...     lambda_2=2,
    ...     mu=2,
    ...     num_of_servers=2,
    ...     threshold=3,
    ...     system_capacity=4,
    ...     buffer_capacity=2,
    ...     seed_num=0,
    ...     runtime=2000,
    ... )
    >>> probs = abg.simulation.get_simulated_state_probabilities(
    ...    simulation_object=simulation_object,
    ... )
    >>> np.round(probs, decimals=3)
    array([[0.166, 0.266, 0.192, 0.147, 0.025],
           [  nan,   nan,   nan, 0.094, 0.024],
           [  nan,   nan,   nan, 0.058, 0.027]])

    >>> np.nansum(probs)
    1.0

Similarly to get the average steady state probabilities over multiple runs,
one can use:

\begin{lstlisting}[style=pystyle]
    >>> import numpy as np
    >>> import ambulance_game as abg
    >>> probs = abg.simulation.get_average_simulated_state_probabilities(
    ...     lambda_1=1,
    ...     lambda_2=2,
    ...     mu=2,
    ...     num_of_servers=2,
    ...     threshold=3,
    ...     system_capacity=4,
    ...     buffer_capacity=2,
    ...     seed_num=0,
    ...     runtime=2000,
    ...     num_of_trials=10,
    ... )
    >>> np.round(probs, decimals=3)
    array([[0.18 , 0.267, 0.197, 0.144, 0.024],
           [  nan,   nan,   nan, 0.085, 0.022],
           [  nan,   nan,   nan, 0.054, 0.026]])

    >>> np.nansum(probs)
    1.0

In the scenario where there are two queueing models and a service that 
distributes individuals to the models, (i.e. the scenario described in this 
paper) the simulation can be used to decide what proportion of individuals 
to send to each the model.
Note that the output of the function shows the value of \(p_1\), the proportion
of class 2 individuals to be sent to queueing model 1.

\begin{lstlisting}[style=pystyle]
    >>> import ambulance_game as abg
    >>> abg.simulation.calculate_class_2_individuals_best_response(
    ...     lambda_2=4,
    ...     lambda_1_1=1,
    ...     lambda_1_2=1,
    ...     mu_1=4,
    ...     mu_2=3,
    ...     num_of_servers_1=2,
    ...     num_of_servers_2=2,
    ...     threshold_1=3,
    ...     threshold_2=3,
    ...     system_capacity_1=3,
    ...     system_capacity_2=3,
    ...     buffer_capacity_1=2,
    ...     buffer_capacity_2=2,
    ...     seed_num_1=0,
    ...     seed_num_2=0,
    ...     num_of_trials=3,
    ...     warm_up_time=100,
    ...     runtime=1000,
    ... )
    0.6343260586929469

@@

\begin{itemize}
    \item \lstinline[style=pystyle]{build_model}: \textit{Builds a ciw object 
    that represents a model of a queuing network with two waiting spaces.}
    \item \lstinline[style=pystyle]{build_custom_node}: \textit{Build a custom 
    node to replace the default ciw.Node. Inherits from the original ciw.Node 
    class and replaces two methods.}
    \item \lstinline[style=pystyle]{simulate_model}: \textit{Simulate the model
    by using the custom node and returning the simulation object}
    \item \lstinline[style=pystyle]{extract_times_from_records}: \textit{Get the
    required times (waiting, service, blocking) out of ciw's records where all 
    individuals are treated the same way}
    \item \lstinline[style=pystyle]{extract_times_from_individuals}: \textit{
    Extract waiting times and service times for all individuals and proceed to 
    extract blocking times for only class 2 individuals}
    \item \lstinline[style=pystyle]{get_list_of_results}: \textit{Modify the 
    outputs so that they are returned in a list format where it is sometimes 
    easier to be used by other functions.}
    \item \lstinline[style=pystyle]{get_multiple_runs_results}: \textit{Get the 
    waiting times, service times and blocking times for multiple runs of the 
    simulation}
    \item \lstinline[style=pystyle]
    {extract_total_individuals_and_the_ones_within_target_for_both_classes}:
    \hfill\break \textit{Extract the total number of individuals that pass 
    through the model and the total number of individuals that exit the model 
    within the given target.}
    \item \lstinline[style=pystyle]
    {get_mean_proportion_of_individuals_within_target_for_multiple_runs}: 
    \textit{Get the average proportion of individuals within target by running 
    the simulation multiple times}
    \item \lstinline[style=pystyle]{get_simulated_state_probabilities}: \textit{
    Calculates the vector \(\pi\) in a dictionary format or an array format}
    \item \lstinline[style=pystyle]{get_average_simulated_state_probabilities}:
    \textit{This function runs \hfill\break
    get\_simulated\_state\_probabilities for multiple iterations to eliminate 
    any stochasticity from the results}
    \item \lstinline[style=pystyle]
    {get_mean_blocking_difference_between_two_systems}: \textit{Given a 
    predefined proportion of class's 2 arrival rate calculate the mean 
    difference between blocking times of two systems with a given set of 
    parameters}
    \item \lstinline[style=pystyle]{calculate_class_2_individuals_best_response}
    \textit{Obtains the optimal distribution of class 2 individuals such that 
    the blocking times in the two systems are identical and thus minimised}
\end{itemize}
